### 2020-01-04 cv_models.tex
moved pdf

\paragraph{Empirical Metrics vs Test Accuracies for VGG}

@@

@@

>>>>

\paragraph{Empirical Metrics vs Test Accuracies for CV models}

@@

VGG works remarkably well

ResNet is also correlated, but the RMSE is much larger, and 2/5 of the models are almost outliers
But note that the PyTorch distribution only has a few models.
The ResNet results look better when considering all ResNet models, trained on ImageNet1K.

@@

Compare VGG, ResNet, and DenseNet in the context of how many connections that have
